---
title: Robin (Guohuibin) Li's Resume
author: Robin (Guohuibin) Li
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)
library(purrr)
library(tidyr)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')


# First let's get the data, filtering to only the items tagged as
# Resume items
position_data <- read_csv('positions.csv') %>% 
  filter(in_resume) 
```




Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------



- <i class="fa fa-envelope"></i> robin.g.li@asu.edu
- <i class="fa fa-twitter"></i> RobinatASU
- <i class="fa fa-github"></i> github.com/lghb2005
- <i class="fa fa-link"></i> [guohuibinli.com](https://guohuibinli.com/)
- <i class="fa fa-phone"></i> +31 (0) 619-731-369


<br>
<br>
<br>

Research Interests {#ResearchInterests}
--------------------------------------------------------------------------------

-	Science & IT Policy
-	Big Data & Algorithm 
-	Information Integrity & Data Ethics
-	Public Surveillance & Privacy 
- Entrepreneurship & Innovation 
-	Organization Theory & Behaviors 
-	Digital Economy & Inequality 
-	Cultural & Geographical Sociology 

<br>
<br>


Skills {#skills}
--------------------------------------------------------------------------------

- R
- Python
- Tableau
- ClickView
- SPSS
- SAP
- LANDESK
- Consulting


<br>


Languages {#languages}
--------------------------------------------------------------------------------

- Mandarin (native)
- English (professional)
- Dutch (some)
- Japaneses (little)
- Uygur (some)



<br>
<br>



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown). 

Source code: [github.com/nstrayer/cv](https://github.com/scarlett425/cv).

Last updated on `r Sys.Date()`.



Main
================================================================================

Robin (Guohuibin) Li {#title}
--------------------------------------------------------------------------------

<br>


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```


Research Projects {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('research_projects')
```

<br>


Teaching Experiences {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('teaching_positions')

```





Publications & Conferences {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}

position_data %>% print_section('publications_conferences')

```


<br>


Professional Membership & Review Experiences {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}

position_data %>% print_section('membership_review')

```


<br>


Other Professional Experience  {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('other_professional_experiences')
```

<br>

Award & Honor  {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}

position_data %>% print_section('award_honor')


```


